### 2014-03-19 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: minor report update

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door. Therefore, further more detailed analysis will focus on the results of the baseline simulation results.

@@

\section{Temperature}
The focus area for analysis of the temperature simulation results are the attic, the rear porch and connecting stairwell, and the interior hallways which connects the rear porch to the front stairwell.

>>>>

From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW). At 130 seconds the rear door is opened in the baseline simulation. At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}). The open door and breach act as additional pressure releases for the structure. Again, the abrupt change in ventilation causes the HRR to spike. Here we see a rise from 7 MW to 9.7 MW at 139 seconds. At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases. While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door. Therefore, the following analysis will focus on the results of the baseline simulation results.

@@

\section{Temperature}
For analysis of the predicted simulation temperatures, the analysis will focus on the high hazard areas of the structure: the attic, the rear porch and connecting stairwell, and the interior hallway which connects the rear porch to the front stairwell. Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions. The first time to consider is just before a firefighter opened the rear porch door (cf. Fig.~(\ref{fig:temp_129s})).
